Supplementary Material for Effects of bariatric surgery and weight loss on resting state functional connectivity

### 2021-02-06 manuscript/supplements_rsfmri.Rmd

---
title: "Supplementary Material for Effects of bariatric surgery and weight loss on resting state functional connectivity"
author:
- Hannah Sophie Heinrichs* [1]
- Frauke Beyer* [1][2]
- Kristin Prehn
- Jürgen Ordemann 
- Agnes Floel
- A. Veronica Witte [1][2][3]
date: 1 Max-Planck-Institute for Human Cognitive and Brain Sciences, Leipzig \newline
  2 CRC 1052 "Obesity Mechanisms", Subproject A1, University of Leipzig \newline 3
  Day Clinic for Cognitive Neurology, University Clinic Leipzig
output:
  bookdown::pdf_book:
    fig_caption: yes
    always_allow_html: true
    number_sections: yes
    toc: no
    extra_dependencies: "subfig"
bibliography: "bibliography.bib"
editor_options:
  chunk_output_type: console
---

@@

# Results
## Quality Control
```{r figtSNR,fig.cap="Lower tSNR in the region of interest NAcc versus precuneus used for seed-based connectivity (shown are all 101 timepoints)", out.width="40%", eval=TRUE}
tsnr <- "../report/tsnr.jpeg"
knitr::include_graphics(tsnr)
```

>>>>

---
title: "Supplementary Material for Effects of bariatric surgery and weight loss on resting state functional connectivity"
author:
- Hannah Sophie Heinrichs* [1]
- Frauke Beyer* [1][2]
- Evelyn Medawar [1]
- Kristin Prehn [3][4]
- Jürgen Ordemann [8][9]
- Agnes Floel [5][6][7]
- A. Veronica Witte [1][2][10]
date: 1 Max-Planck-Institute for Human Cognitive and Brain Sciences, Leipzig \newline
  2 CRC 1052 "Obesity Mechanisms", Subproject A1, University of Leipzig \newline 3 Department of Neurology and NeuroCure Clinical Research Center, Charité University Medicine, Berlin \newline 4 Department of Psychology, Medical School Hamburg, Hamburg \newline 5 Department of Neurology, University of Greifswald, Greifswald \newline 6 German Center for Neurodegenerative Diseases, Standort Rostock/Greifswald, Greifswald \newline 7 Center for Stroke Research, Charité University Medicine, Berlin \newline 8 Center for Bariatric and Metabolic Surgery, Charité University Medicine, Berlin \newline 9 Zentrum für Adipositas und Metabolische Chirurgie, Vivantes Klinikum Spandau, Berlin \newline 10 Day Clinic for Cognitive Neurology, University Clinic Leipzig
output:
  bookdown::pdf_book:
    fig_caption: yes
    always_allow_html: true
    number_sections: yes
    toc: no
    extra_dependencies: "subfig"
bibliography: "bibliography.bib"
editor_options:
  chunk_output_type: console
---

@@

```{r fighistograms,fig.cap="Histograms of FC-QC correlations for different preprocessing schemes)", out.width="40%", eval=FALSE}
tsnr <- "../report/tsnr.pdf"
knitr::include_graphics(tsnr)
```

```{r figtSNR,fig.cap="Lower tSNR in the region of interest NAcc versus precuneus used for seed-based connectivity (shown are all 101 timepoints)", out.width="40%", eval=TRUE}
tsnr <- "../report/tsnr.pdf"
knitr::include_graphics(tsnr)
```
